%
% Shawn-T-Schwartz_CV.tex
% Copyright (c) 2018 Shawn Tyler Schwartz <shawnschwartz@ucla.edu>
% https://shawntylerschwartz.com
%

\documentclass[margin]{res}
% \usepackage{helvetica}
\newsectionwidth{0pt}
\usepackage{fancyhdr}

% \usepackage{hyperref}
\usepackage[hidelinks]{hyperref}

\usepackage{color}
\usepackage[dvipsnames]{xcolor}

\usepackage{multicol}

\makeatletter
\def\section{\@startsection{section}{1}{\z@}{-1.5ex \@plus -1ex \@minus -.2ex}{0.3ex \@plus .2ex}
  {\normalfont\raggedright\large\bfseries}}
\def\subseciton{\@startsection{subsection}{2}{\z@}{-3.25ex\@plus -1ex \@minus -.2ex}{1.5ex \@plus .2ex}
  {\normalfont\raggedright\large\bfseries}}
\def\subsubsection{\@startsection{subsubsection}{3}{\z@}{-3.25ex\@plus -1ex \@minus -.2ex}{1.5ex \@plus .2ex}
  {\normalfont\raggedright\normalsize\bfseries}}
\makeatother

\newcommand\upperv{-5pt}
\newcommand\lowerv{-10pt}

\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{24pt}
\setlength{\headheight}{24pt}
\pagestyle{fancy}
\lfoot{ {\it CURRICULUM VITAE} }
\rhead{ {\it S.T. Schwartz}\\{\it pg. \thepage} }
\rfoot{ {\it Updated 11/2018} }
\cfoot{}
\topmargin=-0.5in


\begin{document}
	\thispagestyle{empty}
	
	\moveleft.5\hoffset\centerline{\LARGE\bf SHAWN T. SCHWARTZ}
	\address{ \centerline{ {\it Modified for Web}, Los Angeles, CA 90024} \\ \centerline{shawnschwartz@ucla.edu $\cdot$ shawntylerschwartz.com $\cdot$ (818) 370-2159}}
	
	\begin{resume}
		% SUMMARY
		\section{SUMMARY}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		A well-rounded undergraduate student and public speaker with 10 years of programming, design, and full-stack development experience, in over 10 programming languages. My research interests include memory differences and deficits in younger adults as well as in the development of innovative teaching technologies to enhance the 21st century classroom education experience.
		
		% EDUCATION
		\section{EDUCATION}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		{\bf University of California, Los Angeles (UCLA)}, Los Angeles, CA \hfill Sept. 2015 \textendash\ Exp. June 2019 
		\vspace{0.01in} 
		\\ {\sl Bachelor of Science (B.S.)}, Cognitive Science, {\it Specialization in Computing}, {\it Expected} June 2019 \\
		\vspace{-0.1mm}
		\hspace{0.25cm} Highest Departmental Honors and Thesis, {\it Candidate} \\
		\vspace{0.01mm}
		\hspace{0.25cm} Thesis: {\it Risks and rewards: memory for positive and negative item-location associations. } \\
		\vspace{0.01mm}
		\hspace{0.17cm} Primary Advisor: Dr. Alan D. Castel
		\vspace{0.75mm}
		\\ {\sl Bachelor of Science (B.S.)}, Biology, {\it Expected} June 2019 \\
		\vspace{-0.1mm}
		\hspace{0.25cm}  Departmental Honors and Thesis, {\it Candidate} \\
		\vspace{0.01mm}
		\hspace{0.25cm} Thesis: {\it Machine learning applications for classifying biodiversity of color-patterns in coral reef fishes. } \\
		\vspace{0.01mm}
		\hspace{0.17cm} Primary Advisor: Dr. Michael Alfaro
		
		% PUBLICATIONS
		\section{PUBLICATIONS}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		%\begin{enumerate}
		%	\item Dang, J., Lin, B., Yuan, J., {\bf Schwartz, S. T.}, Shah, R. M., \& Garg, N. K. (2018). Smart access to 3D structures. {\it Nature Reviews Chemistry}, 1. \textcolor{RoyalBlue}{\url{https://doi.org/10.1038/s41570-018-0021-y}}
		%\end{enumerate}
		
		% https://tex.stackexchange.com/questions/22645/hiding-the-title-of-the-bibliography
		\begingroup
			\renewcommand{\section}[2]{}%
			\begin{thebibliography}{42}
				\bibitem{Schwartz2018}
				Dang, J., Lin, B., Yuan, J., {\bf Schwartz, S. T.}, Shah, R. M., \& Garg, N. K. (2018). Smart access to 3D structures. {\it Nature Reviews Chemistry 2}, 95 \textendash\ 96. \textcolor{RoyalBlue}{\href{https://shawntylerschwartz.com/papers/Smart-Access-to-3D-Structures-Schwartz-2018-Nature-Reviews-Chemistry.pdf}{View PDF}}
				\bibitem{Schwartz2019Memory}
				{\bf Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2019). {\it Risks and rewards: memory for positive and negative item-location associations.} Manuscript in preparation.
			\end{thebibliography}
		\endgroup
		
		% RESEARCH EXPERIENCE
		\section{RESEARCH EXPERIENCE}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		{\bf The Alfaro Lab}, UCLA, Los Angeles, CA  \hfill September 2018 \textendash\ Present \\
		{\it Undergraduate Honors Thesis Student \& Research Assistant} \\
		Principal Investigator: Dr. Michael Alfaro
		\begin{itemize} \itemsep -2pt
			\item My current research with Liz Karan, under Michael Alfaro, Ph.D., focusses on designing novel machine learning image processing algorithms to classifying the biodiversity of color-patterns in coral reef fishes. 
			\item Evolutionary Biology Research Interests: Computational and Comparative Phylogenetic Analyses, Biological Statistical Modeling, Species Biodiversity Classification
		\end{itemize}
		
		{\bf Memory and Lifespan Cognition Lab}, UCLA, Los Angeles, CA  \hfill February 2018 \textendash\ Present \\
		{\it Undergraduate Honors Thesis Student \& Research Assistant} \\
		Principal Investigator: Dr. Alan D. Castel
		\begin{itemize} \itemsep -2pt
			\item My current research with Alexander L. M. Siegel, M.A., under Alan Castel, Ph.D., focusses on establishing differences in the relationships between an item's value and its spatial location to investigate participants' strategies in visuospatial memory recall with risk-reward motivation. 
			\item Other projects include the investigation of priming and interference in everyday memory and attention.
			\item Cognitive Research Interests: Metacognition, Aging, Metamemory, Risk-Reward, Visuospatial Memory
		\end{itemize}
		
		{\bf NASA Jet Propulsion Laboratory (JPL)}, Pasadena, CA \hfill October 2013 \textendash\ March 2014 \\
		{\it High School Computational Chemistry Researcher}
		\begin{itemize} \itemsep -2pt
			\item Developer of Software: {\it ``Computational Simulation of Multidimensional H\textsubscript{2}O Molecule Interactions" (Java + MATLAB)} under the mentorship of Dr. William N. Warner.
			\item First rendition of software won 1st place at L.A. County Science Fair, March 2013.
			\item Competed for invitation to Intel International Science and Engineering Fair at the California State Science Fair, April 2013.
		\end{itemize}
		
		% TECHNICAL & LABORATORY SKILLS
		\section{TECHNICAL \& LABORATORY SKILLS}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{0pt}
		\begin{itemize} \itemsep 2pt
			\item {\bf Programming} 
				\\ {\sl Fluent in} Java, C++, Python, MATLAB, R, PHP, HTML5, CSS3, JavaScript
				\\ {\sl Proficient in} Swift, MySQL, Ruby, JSON, jQuery, AngularJS, Node.js
				\\ {\sl Statistical Packages:} tidy, colordistance, dplyr, pavo, magick
				\\ {\sl Other Libraries \& Tools:} jsPsych, Collector, Psychtoolbox, Jekyll, Jmol, JSmol, p5.js
				\\ {\sl Machine Learning:} TensorFlow, Keras
			\item {\bf Applications}
				\\ Bash, Git, \LaTeX, SPSS Statistics, Microsoft Excel, Sublime Text, R-Studio, Xcode, Jupyter Notebook
				\\ Adobe Photoshop, Adobe Illustrator, Adobe InDesign, Adobe Lightroom, Adobe XD CC
			\item {\bf Operating Systems}
				\\ MacOS, Windows, Linux, iOS, Android
			\item {\bf Statistical}
				\\ Analysis of variance, correlation, chi-square, regression, hierarchical linear modeling (HLM)
			\item {\bf Laboratory}
				\\ Titrations, Micropipetting, Gel Electrophoresis
				\\ Mass Spectrometry, IR, H,C\textendash NMR Analysis
				\\ Functional Neuroimaging (fMRI) \& FMRIB Software Library (FSL)
		\end{itemize}
				
		% TECHNICAL EXPERIENCE
		\section{TECHNICAL EXPERIENCE}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		
		{\bf Associated Students UCLA (ASUCLA)} \hfill Los Angeles, CA \\
		{\it Lead Student Full-Stack Web Developer / Technical Assistant} \hfill January 2016 \textendash\ Present
		\begin{itemize} \itemsep -2pt
			\item Redesigned entire ASUCLA institutional website \& implemented backend for Board Members to access and edit site content. Site reaches over 500,000+ unique views annually. \textcolor{RoyalBlue}{\url{http://asucla.ucla.edu}}
			\item Assisted in designing layout \& developed backend JavaScript solutions for responsive headers on the new UCLA Store e-commerce website. \textcolor{RoyalBlue}{\url{http://uclastore.com}}
			\item Developed a JavaScript kiosk program to run historical timeline of UCLA in UCLA Ackerman Union Level 1.
			\item Designed \& programmed interactive JSON ASUCLA Store Reward Points checker \& PHP-based menus for campus restaurants.
			\item Design, code, and send out weekly mass email promotions for 12 UCLA campus stores {\it (1,000,000+ emails delivered per year)}.
		\end{itemize}
		
		{\bf UCLA Health, Faculty Practice Group (FPG)} \hfill Los Angeles, CA \\
		{\it Population Health Care Coordinator Intern} \hfill June 2017 \textendash\ September 2018
		\begin{itemize} \itemsep -2pt
			\item Invented, developed \& maintained novel web-software for UCLA Health Hospice \& Palliative Care Departments: {\it myEMRA\textsuperscript{\textregistered}: ``my Electronic Matching Resource Assistant"}.  \\ {\sl *Adoption \& Pilot by UCLA Health System \& ISS for proxied network integration currently in progress.*}
			\item Outreached to patients via telephone encounters to obtain missing medical procedure records.
			\item Maintained innovative Excel Database from UCLA patients' charts (``CareConnect") \& 9 local hospice agencies for tracking \& drawing new statistical conclusions regarding UCLA hospice referrals to external agencies.
			\item {\bf Total Volunteered Hours: 451 hours.}
		\end{itemize}
		
		{\bf QR Chemistry} \hfill Los Angeles, CA \\
		{\it Software Development Consultant \& Application Designer} \hfill January 2018 \textendash\ July 2018
		\begin{itemize} \itemsep -2pt
			\item Part of the development \& execution team of an Apache Cordova wrapped application that provides smart access to 3D molecular structures for enhancing organic chemistry education in the classroom. \textcolor{RoyalBlue}{\url{https://qrchem.net}}
			\item Developed with the guidance \& support of Dr. Neil K. Garg \& Dr. Daniel Caspi. \\Published in {\it Nature Reviews Chemistry}, [1] \& Supporting Article in \textcolor{RoyalBlue}{\href{https://dailybruin.com/2018/07/30/student-developed-tool-brings-3d-molecular-models-to-smartphone-screen/}{\it The Daily Bruin}}.
		\end{itemize}
		
		{\bf Kidz Dental Care} \hfill Porter Ranch, CA \\
		{\it Designer \& Web Developer} \hfill July 2017 \textendash\ June 2018
		\begin{itemize} \itemsep -2pt
			\item Designed, built, and currently maintains (per diem) pediatric dentistry's responsive websites. \\ \textcolor{RoyalBlue}{\url{https://kidzdentalcare.com}} \& \textcolor{RoyalBlue}{\url{https://kidzdentalcare661.com}}
			\item Created HIPAA-compliant secure patient information pipeline (PHP) that generates \& transmits \\ secured PDF information form to streamline patient-doctor experience and reduce wait-times.
		\end{itemize}
		\vspace{0.02cm} 
		{\bf LanguageBird\textsuperscript{\textregistered}, LLC} \hfill Los Angeles, CA \\
		{\it Lead Full-Stack Developer \& Programmer} \hfill July 2016 \textendash\ March 2018
		\begin{itemize} \itemsep -2pt
			\item Developed and managed dynamic user experience for WASC accredited online school providing WASC, University of California, and NCAA approved online 1:1 foreign language courses and credit to over 1000 high school students, worldwide. \textcolor{RoyalBlue}{\url{https://languagebird.com}}
		\end{itemize}
		
		% VOLUNTEER EXPERIENCE
		\section{VOLUNTEER EXPERIENCE}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		{\bf UCLA Health} \hfill Santa Monica, CA \\
		{\it Care Extender Internship, Department Coordinator Assistant (DCA)} \hfill February 2017 \textendash\ Present
		\begin{itemize} \itemsep -2pt
			\item Shadow out-patient surgeons and radiology technicians for in-patient and emergency department cases, and check-in patients for early-morning surgeries in admissions.
			\item {\it Department Coordinator Assistant:} Audit fellow Care Extender Volunteers throughout their assigned departments to maintain the quality and integrity of the Care Extender Internship Program.
			\item {\bf Total Volunteered Hours: 783 hours.}
		\end{itemize}
		
		{\bf UCLA Center for Accessible Education (CAE)} \hfill Los Angeles, CA \\
		{\it Volunteer Notetaker} \hfill January 2017 \textendash\ Present \\
		Provided quality, detailed notes for students with registered disabilities, for the following courses:
		\begin{itemize} \itemsep -2pt
			\item Psychology 20A: Introduction to MATLAB Programming (Winter 2017)
			\item Psychology 100B: Research Methods in Psychology (Fall 2017)
			\item Psychology 124C: Human Memory (Winter 2018)
			\item Ecology and Evolutionary Biology 186: Evolutionary Medicine (Summer 2018)
		\end{itemize}
		
		% LEADERSHIP EXPERIENCE
		\section{LEADERSHIP EXPERIENCE}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		{\bf Back Off Bully Organization} \hfill Chatsworth, CA \\
		{\it Co-Founder \& Web Developer} \hfill March 2014 \textendash\ Present \\
		{\sl Back Off Bully is an organization that is working to end the bullying epidemic and give self-confidence to those affected by it.}
		\begin{itemize} \itemsep -2pt
			\item Built an international network, in over four countries, of thousands of children and adults through website outreach and social media campaigns. 
			\item Established connection and relationship, through outreach, with our organization's Main Sponsor: {\bf Nancy Cartwright} (Voice of Bart Simpson from {\bf \it The Simpsons}). \textcolor{RoyalBlue}{\url{https://backoffbully.org}}
		\end{itemize}
		
		% AWARDS AND PROFESSIONAL MEMBERSHIPS
		\section{AWARDS \& PROFESSIONAL MEMBERSHIPS}
		\vspace{\upperv}
		\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
		\vspace{\lowerv}
		{\bf Awards:}
		\begin{itemize} \itemsep -2pt
			\item Highest Departmental Thesis Honors in Psychology, {\it UCLA}, Exp. June 2019
			\item Departmental Thesis Honors in Ecology and Evolutionary Biology, {\it UCLA}, Exp. June 2019
			\item Distinguished Care Extender of the Rotation, {\it UCLA Health, Santa Monica Hospital Surgery Center}, October 2018
			\item Distinguished Community Service Award \& Rank 1/81 Valedictorian, {\it High Tech Los Angeles High School}, June 2015
			\item Certificate of Congressional Recognition for outstanding community contribution to end the bullying epidemic and provide self-confidence for those affected by it, {\it City of L.A. \& 12th Council District}, July 2014
		\end{itemize}
		
		{\bf Professional Memberships:}
		\begin{itemize} \itemsep -2pt
			\item American Psychological Association (APA), {\it Undergraduate Student Affiliate}, \\ {\it Member: American Psychological Association of Graduate Students (APAGS)}
			\item Association for Psychological Science (APS), {\it Undergraduate Student Affiliate}
		\end{itemize}
		
		\end{resume}
\end{document}