\section{CONFERENCE PRESENTATIONS AND INVITED TALKS}
\vspace{\upperv}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
\vspace{\lowerv}
Siegel, A. L. M., {\bf Schwartz, S. T.}, \& Castel, A. D. (2020, April). {\it Age-related differences in local and global metacognitive accuracy in a visuospatial selectivity task.} Poster to be presented at the Cognitive Aging Conference in \\
Atlanta, GA, USA. April 16.

{\bf Schwartz, S.T.}, \& Alfaro, M. E. (2019, November). {\it High-throughput phenoscaping using deep learning for accurate automatic instance segmentation of fish images.} Poster presented at the UCLA Institute for Digital Research and Education Early Career Research Day in Los Angeles, CA, USA. November 20. \textbf{\textit{*Best Poster Award}}

Siegel, A. L. M., {\bf Schwartz, S. T.}, \& Castel, A. D. (2019, November). {\it Memory and metamemory for the location of items: The effects of information importance and encoding difficulty.} Poster presented at the Psychonomic Society's 60th Annual Meeting in Montréal, Quebec, Canada. November 16.

Whatley, M. C., {\bf Schwartz, S. T.}, Block, J. B., Siegel, A. L. M., \& Castel, A. D. (2019, November). {\it One bad apple: Visual memory and misinformation for the Apple logo.} Poster presented at the Psychonomic Society's 60th Annual Meeting in Montréal, Quebec, Canada. November 15.

{\bf Schwartz, S. T.}, Karan, E. A., \& Alfaro, M. E. (2019, May). {\it Using machine learning to quantify color pattern diversity in Butterflyfishes (Chaetodontidae).} Poster presented at the 22nd Annual UCLA Biology Research Symposium in Los Angeles, CA, USA. May 22.

{\bf Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2019, May). {\it Risks and rewards: Memory for positive and negative item-location associations.} Poster presented at the 22nd UCLA Annual Undergraduate Research Poster Day in Los Angeles, CA, USA. May 21. \textbf{\textit{*UCLA Dean's Research Prize Nominee}}

{\bf Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2019, May). {\it Risks and rewards: Memory for positive and negative item-location associations.} Poster presented at the 28th Annual UCLA Psychology Undergraduate Research Conference in Los Angeles, CA, USA. May 10.

{\bf Schwartz, S. T.}, Siegel, A. L. M., \& Castel, A. D. (2019, May). {\it Memory for positive and negative item-location associations.} Poster presented at Whittier College's 17th Annual Psi Chi Psychology Undergraduate Research Conference in Whittier, CA, USA. May 4.

Karan, E. A., \& {\bf Schwartz, S. T.} (2019, May). {\it Quantitative approaches to studying color pattern evolution.} Guest Lecture given at Claremont McKenna College, Biology Department in Claremont, CA, USA. May 2.

{\bf Schwartz, S. T.} (2019, May). {\it Risks and rewards: Memory for positive and negative item-location associations.} Departmental Highest Honors Thesis Seminar Talk given at the UCLA Department of Psychology in Los Angeles, CA, USA. May 1.