\section{MEDICAL VOLUNTEER EXPERIENCE \hfill {\small (1,315 Medical Volunteer Hours)}}
\vspace{\upperv}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
\vspace{\lowerv}
{\bf UCLA Health \hfill Santa Monica, CA} \\
{\it Care Extender Internship, Department Coordinator Assistant (DCA)} \hfill January 2017 \textendash\ February 2019
\begin{itemize} \itemsep -2pt
	\item Shadowed out-patient surgeons and radiology technicians for in-patient and emergency department cases, and checked in patients for early-morning surgeries in admissions.
	\item {\it Department Coordinator Assistant:} Audited fellow Care Extender Volunteers throughout their assigned departments to maintain the quality and integrity of the Care Extender Internship Program.
	\item Volunteered 814 hours.
\end{itemize}

{\bf UCLA Health, Faculty Practice Group (FPG) \hfill Los Angeles, CA} \\
{\it Population Health Care Coordinator Intern} \hfill June 2017 \textendash\ September 2018
\begin{itemize} \itemsep -2pt
	\item Outreached to patients via telephone encounters to obtain missing medical procedure records.
	\item Maintained innovative Excel Database from UCLA patients' Electronic Medical Records (``CareConnect") and 9 local hospice agencies for tracking and drawing new statistical conclusions regarding UCLA hospice referrals to external agencies.
	\item Volunteered 451 hours.
\end{itemize}

{\bf Providence Tarzana Medical Center \hfill Tarzana, CA} \\
{\it Engineering Facilities Intern} \hfill September 2014 \textendash\ January 2015
\begin{itemize} \itemsep -2pt
	\item Assisted clinical staff with errands, clerical duties, and medical technology-related problems; helped patients with ambulatory tasks; discharged patients.
	\item Volunteered 50 hours.
\end{itemize}