\section{RESEARCH EXPERIENCE}
\vspace{\upperv}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt}\smallskip
\vspace{\lowerv}
{\bf Alfaro Lab}, UCLA Department of Ecology and Evolutionary Biology \hfill {\bf Los Angeles, CA} \\
{\it Graduate Student Researcher} \hfill September 2019 \textendash\ Present \\
{\it Undergraduate Honors Thesis Research Assistant} \hfill September 2018 \textendash\ August 2019 \\
Principal Investigator: Dr. Michael E. Alfaro
\begin{itemize} \itemsep -2pt
	\item Designed a novel machine learning pipeline to quantify evolution of color pattern in reef fishes.
	\item Actively mentor undergraduate students while conducting master's thesis research.
\end{itemize}

{\bf Memory and Lifespan Cognition Lab}, UCLA Department of Psychology \hfill {\bf Los Angeles, CA} \\
{\it Graduate Student Collaborator} \hfill September 2019 \textendash\ Present \\
{\it Undergraduate Highest Honors Thesis Research Assistant} \hfill February 2018 \textendash\ August 2019 \\
Principal Investigator: Dr. Alan D. Castel
\begin{itemize} \itemsep -2pt
	\item Developed computational approaches to study value-directed remembering and visuospatial memory.
	\item Expanding computational paradigms to investigate memory and metamemory in visuo- and audio-spatial domains.
\end{itemize}

{\bf Foster Lab}, UCLA Department of Sociology \hfill {\bf Los Angeles, CA} \\
{\it Undergraduate Research Assistant} \hfill January 2019 \textendash\ June 2019 \\
Principal Investigator: Dr. Jacob G. Foster 
\begin{itemize} \itemsep -2pt
	\item Studied cultural evolution by investigating rates of speciation and diversification of television shows.
\end{itemize}

{\bf Garg Lab}, UCLA Department of Chemistry and Biochemistry \hfill {\bf Los Angeles, CA} \\
{\it Undergraduate Software Research Consultant} \hfill January 2018 \textendash\ July 2018 \\
Principal Investigator: Dr. Neil K. Garg
\begin{itemize} \itemsep -2pt
	\item Co-developed a novel tool for visualizing 3D molecular structures interactively in large-lectures and research conference poster sessions through a custom written interface and unique QR code generator application. \\ \textcolor{RoyalBlue}{\href{https://qrchem.net}{https://qrchem.net}}
\end{itemize}

{\bf NASA Jet Propulsion Laboratory (JPL)} \hfill {\bf La Cañada Flintridge, CA} \\
{\it Computational Chemistry Researcher} \hfill October 2013 \textendash\ March 2014 \\
Mentor: Dr. William N. Warner \\